Normal States Training for High Accuracy Event Detection

### 2016-06-17 paper/ieeeFormat.tex
fix figure 6

\documentclass[conference,compsoc]{IEEEtran}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
%\usepackage{algorithm}
\usepackage{bm}%used for bm
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath} %used for maths symbols
\usepackage{amssymb}%used for empty set symbol

@@

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
And further experiments on \textit{reddit} also demonstrate that \textsc{NSDetector} can be easily adapted on other cyberspace datasets.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

%The event detection task always tries to find out the newsworthy messages from cyberspace. 
With the increasing of cyberspace data nowadays, there is a growing need for detecting events accurately. Detecting events can mainly benifit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

@@

They build the normal states in the evolving training window
%TODO

They are hamppered by the rapid changing nature of cyberspace, e.g. twitter and reddit(\textit{find out the sentences to describe the rapid changing nature}).

It is hard to handle all the cyberspace data by using limited computing resources. As a result, it have to make a trade off, only to process part of them, instead of using the whole data.

In this paper, we demonstrate that the better normal states  are learned, the better event detection system can perform.

 and \textit{full history info enhanced normal states training}.

@@

\section{Related Works}

To train the normal states, the methods of existing systems can be grouped into two categories: \textit{unsupervised normal states training} and \textit{classification based normal states training}, which is illustrated by Figure \ref{fig:modelDesc:a}.

@@

In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
But they are different from ours.
As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as micorblogs.
Instead, we gather user's self-description and the followings' self-description as user profile which is stable to characterize user interests. 
Based on this fine-grained user modeling information, user's long term interest related tweets and short term bursty event related tweets can be distinguished in online style, and can be efficiently applied on microblogs.

Since user modeling has the significant impact on users' activities on microblogs, the usage of user modeling has drawn attention in many research fields. 
\cite{zhao2013inferring} exploits user modeling information and network topology to infer user's role in social network.
\cite{yoshida2013toward} also introduces user modeling to community detection where some edges are not observable, but user profile can provide additional information.
Different from the above work, we do not only treat the user modeling result as an additional feature, but also an important representative factor for users, who are the source of information in microblogs.

User modeling can be carried out to obtain web users' demographics information \cite{culotta2015predicting} (e.g., gender, age, ethnicity, education, income, etc.).
Compared with demographics information, user interests' modeling can be verified more easily \cite{faralli2015large}.

Twitter Trending Topic Classification
%\begin{figure}
%    \includegraphics[height=7.7cm]{img/mlab_dirichlet_alpha_effects.pdf}
%\end{figure}
We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.

%3*4 figures
\begin{figure*}[ht]
        \centering
        \label{fig:subfig} %% label for entire figure
        \subfigure[\(\alpha=(0.25,0.25,0.25)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph0.pdf}
        }
        \subfigure[\(\alpha=(0.5,0.5,0.5)\)]{
                \label{fig:subfig:b} %% label for second subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph1.pdf}
        } 
        \subfigure[\(\alpha=(1.5,1.5,1.5)\)]{
                \label{fig:subfig:c} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph2.pdf}
        }
        \subfigure[\(\alpha=(2.5,2.5,2.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph3.pdf}
        }\hspace{1in}
        \subfigure[\(\alpha=(0.25,0.25,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph4.pdf}
        }
        \subfigure[\(\alpha=(0.5,0.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph5.pdf}
        }
        \subfigure[\(\alpha=(1.5,1.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph6.pdf}
        }
        \subfigure[\(\alpha=(2.5,2.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph7.pdf}
        }\hspace{1in}
        \subfigure[\(\alpha=(0.25,0.75,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph8.pdf}
        }
        \subfigure[\(\alpha=(0.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph9.pdf}
        }
        \subfigure[\(\alpha=(1.5,2.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph10.pdf}
        }
        \subfigure[\(\alpha=(2.5,3.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=3.21cm]{img/croppedDirichletGraph11.pdf}
        }
        \caption{Illustration of Drichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a-d) (e-h) (i-l)}
\end{figure*}

@@

%TODO
\begin{figure}
    \centering
    \includegraphics[width=1.0\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

\subsection{Normal States' Maintenance}
KB-Prior-LDA
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{model/lda_tikz.pdf}
    \caption{Probabilistic model for training normal states by using history information.}
    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
    \label{fig:cnn}
\end{figure}

@@

\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
\lambda \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:initProbability}
\begin{aligned}
\hat{q}_{k|v}=
\left\{ \begin{aligned}
\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 \\
0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} \\
1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}}
\end{aligned}\right.
\end{aligned}
\end{equation}

\begin{equation}
\label{eq:KBPriorLDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}

@@

\begin{algorithm}
\caption{Spectral Clustering Based Event Phrase Extraction}
\label{alg:eventKeywordsSearchMethod}
\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\tau\)}
\KwOut{\(\mathcal{C}_{k,t}\)}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\tau\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

@@

\section{Experiments}
\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{History State Portion}
\end{figure}
\begin{table}
\centering
\caption{Normal State Training Performance}
\label{my-label}
\scalebox{1.0}{
    \begin{tabular}{|l|l|l|}
    \hline
    Model & History State & PMI \\ \hline
    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
    NST\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
    NST         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
    \end{tabular}
}
\end{table}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
\begin{tabular}[c]{@{}c@{}}History\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}History \\ State\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal \\ State\end{tabular} \\ \hline
Army & killed & aircraft & air & medical & weight & league & season \\ 
Battle & news & train & plane & patients & loss & season & win \\ 
military & \#libya & airport & flight & treatment & diet & club & team \\ 
Forces & libya & station & time & disease & pain & cup & deal \\ 
attacks & rebels & flight & ship & health & cancer & football & year \\ 
terrorist & people & pilot & news & brain & health & game & sign \\ 
troops & police & aviation & boat & cancer & lose & games & jagr \\ 
Killed & war & gear & airport & patient & tips & round & richards \\ 
soldiers & libyan & passenger & force & blood & treatment & championship & cup \\ 
commander & attack & drive & fly & body & fat & player & time \\ 
Front & u.s. & navigation & hurricane & clinical & hair & match & arsenal \\ 
Units & gaddafi & departure & navy & care & skin & division & fans \\ 
captured & army & takeoff & coast & surgery & body & win & nasri \\ 
campaign & forces & aviator & home & research & healthy & goals & city \\ 
fighting & pakistan & navigator & crash & type & surgery & teams & league \\ 
siege & afghanistan & runaway & irene & syndrome & blood & play & players \\ 
officers & military & departure & train & system & brain & stadium & player \\ 
guards & attacks & airbus & sea & medicine & acne & coach & signed \\ 
allied & troops & miles & aircraft & eye & diabetes & players & contract \\ 
lieutenant & dead & landing & jet & physician & eye & record & run \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
UMass System & 0.882 & 0.138 & 0.941 & 0. 071 \\ \hline
LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
Our Method & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
\end{tabular}
\end{table*}

\begin{table}[]
\centering
\caption{Twitter data set description}
\label{my-label}
\begin{tabular}{|l|r|}
\hline
Time range & \begin{tabular}[c]{@{}r@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
Tweet number & 36,627,434 \\ \hline
Event number in Benchmark1 & 17 \\ \hline
Event number in Benchmark2 & 523 \\ \hline
\end{tabular}
\end{table}
% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \begin{tabular}{|l|l|l|l|}
% \hline
% \multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Time \\ range\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Tweet \\ number\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark1\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark2\end{tabular}} \\ \hline
% \begin{tabular}[c]{@{}l@{}}2011/06/30-\\ 2011/09/15\end{tabular} & 36,627,434 & 17 & 523 \\ \hline
% \end{tabular}
% \end{table}

@@

\subsection{Data set}
Dataset
We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
We collect the tweets' contents according to the IDs with the help of Twitter API. 
The dataset contains 36,627,434 tweets which spans from 2011/06/30 to 2011/09/15.

>>>>

\documentclass[conference,compsoc]{IEEEtran}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

\usepackage{bm}%used for bm
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath} %used for maths symbols
\usepackage{amssymb}%used for empty set symbol
\usepackage{url}

@@

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) balanced for effectiveness and efficiency, normal states are trained as topical words and their chi-squared scores, and initialized by knowledge base; 2) topical word frequencies on targeted corpus within the time window are learned by NS-Prior-LDA, using the normal states as prior; 3) events are detected by monitoring the change of topical word frequencies; 4) normal states are further maintained by detected events incrementally.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

@@

%The event detection task always tries to find out the newsworthy messages from cyberspace. 
With the increasing of cyberspace data, there is a growing need for detecting events accurately. Detecting events can mainly benifit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

Considering the importance of event detection on the cyberspace data, researchers have have made many efforts, including checking the and the . Therefore, the existing methods are ... and

@@

@@

\section{Related Works}
\subsection{Event Detection}

To train the normal states, the methods of existing systems can be grouped into unsupervised methods and supervised methods based on whether they .

@@

In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
But they are different from ours.
As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as micorblogs.
\subsection{Knowledge Base}

%Twitter Trending Topic Classification
%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.

%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
%2, 3, 6, 7, 10, 11;
\begin{figure*}[ht]
        \centering
        \label{fig:subfig} %% label for entire figure
        \subfigure[\((0.25,0.25,0.25)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
        }
        \subfigure[\((0.5,0.5,0.5)\)]{
                \label{fig:subfig:b} %% label for second subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
        } 
        \subfigure[\((1.5,1.5,1.5)\)]{
                \label{fig:subfig:c} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
        }
        \subfigure[\((2.5,2.5,2.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
        }
        \subfigure[\((0.25,0.25,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
        }
        \subfigure[\((0.5,0.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
        }\hspace{1in}
        \subfigure[\((1.5,1.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
        }
        \subfigure[\((2.5,2.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
        }
        \subfigure[\((0.25,0.75,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
        }
        \subfigure[\((0.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
        }
        \subfigure[\((1.5,2.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
        }
        \subfigure[\((2.5,3.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
        }\hspace{1in}
        \caption{Illustration of Drichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a-d) (e-h) (i-l)}
\end{figure*}

@@

%TODO

\begin{figure}
    \centering
    \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

\subsection{Normal States' Maintenance}
KB-Prior-LDA
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\columnwidth]{model/lda_tikz.pdf}
    \caption{Probabilistic model for training normal states by using history information.}
    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
    \label{fig:cnn}
\end{figure}

@@

\begin{scriptsize}
\begin{equation}
\label{eq:wikiPrior}
\begin{aligned}
\tau_{kv}=
\left\{ \begin{aligned}
\lambda \frac{f_{kv}}{\sum_{v\in S_{kv}}f_{kv}} &,v\in S_{k}\ and  \ k \leq K_{\bm{KB}} \\
0&,v \notin S_{k} \ or \ k > K_{\bm{KB}} \\
\end{aligned}\right.
\end{aligned}
\end{equation}
\end{scriptsize}

\begin{scriptsize}
\begin{equation}
\label{eq:initProbability}
\begin{aligned}
\hat{q}_{k|v}=
\left\{ \begin{aligned}
\frac{\tau_{kv}}{\sum_{k=1}^{K}\tau_{kv}} &,\sum_{k}\tau_{kv}>0 \\
0&, \sum_{k}\tau_{kv}=0 \ and \ k \leq K_{\bm{KB}} \\
1/(K-K_{\bm{KB}})&,\sum_{k}\tau_{kv}=0 \ and \ k > K_{\bm{KB}}
\end{aligned}\right.
\end{aligned}
\end{equation}
\end{scriptsize}

\begin{scriptsize}
\begin{equation}
\label{eq:KBPriorLDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto (n^{(d)}_{dk}+\alpha m_k)\frac{n^{(w)}_{kv}+\tau_{kv}+\beta}{n^{(w)}_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}
\end{scriptsize}

@@

\begin{algorithm}
\caption{Spectral Clustering Based Event Phrase Extraction}
\label{alg:eventKeywordsSearchMethod}
\KwIn{\(\mathcal{B}_{k,t},\mathcal{G}_{k,t},\rho\)}
\KwOut{\(\mathcal{C}_{k,t}\)}
\(n_{k,t}\)=number of connected component in \(\mathcal{G}_{k,t}\)\\
\For{\(n \in \{ n_{k,t}, \cdots, |\mathcal{G}_{k,t}|\}\) }{
    \(\mathcal{C}_{k,t}=SpectralClustering(\mathcal{G}_{k,t},n)\)\\
    \If{\(min_{i\in \{1,\cdots,n\}} Density(\mathcal{C}_{k,t,i},\mathcal{G}_{k,t})>\rho\)}{
        return \(\mathcal{C}_{k,t}\)
    }
}
\end{algorithm}

@@

\section{Experiments}
\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\). The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
\end{figure}

\begin{table}
\centering
\caption{NS-Prior-LDA's Performance on the evaluation metric PMI}
    \begin{tabular}{|l|l|l|}
    \hline
    Model & History State & PMI \\ \hline
    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Learned by LDA}\\ \footnotesize{from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Derived from Categories} \\\footnotesize{of Wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
    \end{tabular}
\label{tbl:NS-Prior-LDA}
\end{table}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Sport}} \\ 
\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ \hline
Army & killed & aircraft & air & medical & weight & league & season \\ 
Battle & news & train & plane & patients & loss & season & win \\ 
military & \#libya & airport & flight & treatment & diet & club & team \\ 
Forces & libya & station & time & disease & pain & cup & deal \\ 
attacks & rebels & flight & ship & health & cancer & football & year \\ 
terrorist & people & pilot & news & brain & health & game & sign \\ 
troops & police & aviation & boat & cancer & lose & games & jagr \\ 
Killed & war & gear & airport & patient & tips & round & richards \\ 
soldiers & libyan & passenger & force & blood & treatment & championship & cup \\ 
commander & attack & drive & fly & body & fat & player & time \\ 
Front & u.s. & navigation & hurricane & clinical & hair & match & arsenal \\ 
Units & gaddafi & departure & navy & care & skin & division & fans \\ 
captured & army & takeoff & coast & surgery & body & win & nasri \\ 
campaign & forces & aviator & home & research & healthy & goals & city \\ 
fighting & pakistan & navigator & crash & type & surgery & teams & league \\ 
siege & afghanistan & runaway & irene & syndrome & blood & play & players \\ 
officers & military & departure & train & system & brain & stadium & player \\ 
guards & attacks & airbus & sea & medicine & acne & coach & signed \\ 
allied & troops & miles & aircraft & eye & diabetes & players & contract \\ 
lieutenant & dead & landing & jet & physician & eye & record & run \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\subtable[Twitter Dataset Statistics]{
\begin{tabular}{|l|r|}
\hline
Time range & \begin{tabular}[c]{@{}l@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
Tweet Number & 36,627,434 \\ \hline
\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark1\end{tabular} & 27 \\ \hline
\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark2\end{tabular} & 523 \\ \hline
\end{tabular}
}\quad \quad
\subtable[Event Detection Results]{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\end{table*}

% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \begin{tabular}{|l|l|l|l|}
% \hline
% \multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Time \\ range\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Tweet \\ number\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark1\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Event number \\ in Benchmark2\end{tabular}} \\ \hline
% \begin{tabular}[c]{@{}l@{}}2011/06/30-\\ 2011/09/15\end{tabular} & 36,627,434 & 17 & 523 \\ \hline
% \end{tabular}
% \end{table}

@@

\subsection{Data set}
Dataset
We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
We collected the tweets' contents according to the IDs with the help of Twitter API. 
Though it's mentioned that there are 90 million tweets, due to the limit of twitter API w
The dataset contains 36,627,434 tweets which spans from 2011/06/30 to 2011/09/15.

%TODO
The benchmark of Edinburgh contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}}.
